---
title: "Data 605 HW 9"
author: "Yohannes Deboch"
date: "27/03/2019"
output: html_document
---

#1. 11 The price of one share of stock in the Pilsdorff Beer Company (see Exer- cise 8.2.12) is given by Yn on the nth day of the year. Finn observes that the differences Xn = Yn+1 − Yn appear to be independent random variables with a common distribution having mean μ = 0 and variance σ2 = 1/4. If Y1 = 100, estimate the probability that Y365 is

```{r}
365*0.25
```

The probability distribution is given by N(100,91.25)

(a) ≥ 100. 

Answer:
```{r}
pnorm(100-100,0,sqrt(91.25))
```

(b) ≥ 110.

Answer:
```{r}
pnorm(110-100,0,sqrt(91.25), lower.tail = F)

```

(c) ≥ 120.

Answer:
```{r}
pnorm(120-100,0,sqrt(91.25), lower.tail = F)

```

#2. Calculate the expected value and variance of the binomial distribution using the moment generating function.

Answer:

$g(t) = \sum_{j=0}^n e^{tj} {{n}\choose{j}}p^jq^{n-j}$

$g(t) = \sum_{j=0}^n {{n}\choose{j}}(pe^t)^jq^{n-j}$

$g(t) = (pe^t+q)^n$

$g'(t) = n(pe^t+q)^{n-1}pe^t$

$g''(t) = n(n-1)(pe^t+q)(pe^t)^2 + n(pe^t+q)^npe^t$

$g'(0) = n(p+q)^{n-1}p =np$

$g''(0) = n(n-1)p^2 + np$

$\boxed{\mu = \mu_1 = g'(0) = np}$

$\sigma^2 = \mu_2-\mu_1^2 = g''(0) - g'(0)^2$

$\sigma^2 = n(n-1)p^2 + np - (np)^2$

$\sigma^2 = np[(np-p) +1 -np]$

$\boxed{\sigma^2 = np[1-p]}$

since p + q = 1.


# 3. Calculate the expected value and variance of the exponential distribution using the moment generating function.

Answer:

$g(t) = \int_0^\infty e^{tx}\lambda e^{-\lambda x} dx$

=>$g(t) = \frac{\lambda e^{(t-\lambda )x}}{t -\lambda}|_0^{\infty}$

=>$g(t) = \frac{\lambda}{\lambda-t}$

Taking first derivative and equating to 0 we find

$g'(t) = \frac{\lambda}{(\lambda-t)^2}$

$g'(0) = \frac{\lambda}{\lambda^2} = \frac{1}{\lambda}$

Taking second derivative and equating to 0 we find

$g''(t) = \frac{2\lambda}{(\lambda-t)^3}$

$g''(0) =  \frac{2\lambda}{\lambda^3} = \frac{2}{\lambda^2}$


Hence
mean

$\mu = g'(0) = \lambda^{-1}$

variance : 
$\mu_{2} - \mu_{1}^2$ = 

$\sigma^2 = g''(0) - g'(0)^2 = \frac{2}{\lambda^2} - \frac{1}{\lambda^2} = \lambda^{-2}$
